Notes on Perturbational Quantities

### 2008-10-24 docs/pert_notes/pert.tex
continue consolidation of macros - there are still some inconsistencies between documents

\subsubsection{Advancing $\rho h$}
{\bf What the did before 8/6/08:}
\begin{equation}
\frac{\partial(\rho h)}{\partial t} = -\nabla\cdot\left[(\rho h)'\left(\Ubt 
+ w_0\eb_r\right)\right] - \nabla\cdot\left[(\rho h)_0^{n+\half,{\rm avg}}\Ubt\right] 
\underbrace{- \nabla\cdot\left[(\rho h)_0^{n+\half,{\rm pred}}w_0\eb_r\right] + \psi}_{\text{this term used to come in through} ~ (\rho h)_0^{n+1} - (\rho h)_0^n} + (\ut \cdot \er)\frac{\partial p_0}{\partial r} \enskip .
\end{equation}
{\bf What the code does now:} We would like to update the non-forcing
part of the enthalpy equation analogously to Section \ref{Advancing
rhoX_k}
\begin{equation}
\frac{\partial(\rho h)}{\partial t} = -\nabla\cdot(\rho h\Ub) = 
-\nabla\cdot\left\{\left[(\rho h)_0^{n+\half,{\rm avg}} 
+ (\rho h)'\right]\left(\Ubt + w_0\eb_r\right)\right\} + (\ut \cdot \er)\frac{\partial p_0}{\partial r} + \psi  \enskip .
\end{equation}

@@

\begin{table*}[h]
\begin{center}
\caption{Forcing term into {\tt make\_edge\_scal} \newline}
\begin{tabular}{c|c}
\hline
\hline
{H PRED TYPE} &   {Force} \\
\hline \\[-3mm]
1  $((\rho h)^\prime)$ &  $(\ut \cdot \er) \frac{\partial p_0}{\partial r} - 
 (\rho h)^\prime \; \nabla \cdot (\ut+w_0 \er) - 
 \nabla \cdot (\ut (\rho h)_0) + \nabla \cdot \kth \nabla T$ \\[2 mm]
2  $(h)$ & $\frac{1}{\rho} \left [\psi + (\ut \cdot \er)
  \frac{\partial p_0}{\partial r} + \nabla \cdot \kth \nabla T \right ]$ \\[2 mm]
3  $(T)$ & $\frac{1}{\rho c_p} \left \{ (1 - \rho h_p) 
   \left [\psi + (\ut \cdot \er) \frac{\partial p_0}{\partial r} \right ] \nabla \cdot \kth \nabla T \right \}$ \\[2 mm]
4  $(T)$ & $\frac{1}{\rho c_p} \left\{ (1 - \rho h_p) \left [\psi + (\ut \cdot \er)
\frac{\partial p_0}{\partial r}\right ] \nabla \cdot \kth \nabla T \right\}$ \\[2 mm]
\hline
\end{tabular}
\end{center}
\end{table*}

@@

\begin{table*}
\begin{center}
\caption{Quantity that is created in {\tt mkflux} and passed into {\tt update\_scal}\newline\
}
\begin{tabular}{c|c|c|c|c}
       &            &              &\multicolumn{2}{c}{Forcing Term} \\
{type} & {Species } & {$(\rho h)$} & {$(\rho X)$} & {$(\rho h)$} \\
\hline 
1 & $(\ut+w_0)(\rho_0+\rho^\prime) X          $ & $(\ut+w_0)\left [(\rho h)_0 + (\rho h)^\prime\right]$ & 0 & $ \psi + (\ut \cdot \er) \frac{\partial p_0}{\partial r} $ \\[2mm]
2 & $(\ut+w_0)(\rho_0+\rho^\prime) X          $ & $(\ut+w_0) (\rho_0+\rho^\prime) h$ & 0 & $ \psi + (\ut \cdot \er) \frac{\partial p_0}{\partial r} $ \\[2mm]
3 & $(\ut+w_0)(\rho_0+\rho^\prime) X          $ & $(\ut+w_0)\left [(\rho h)_0 + (\rho h)^\prime\right]$ & 0 & $ \psi + (\ut \cdot \er) \frac{\partial p_0}{\partial r}$ \\[2mm]
4 & $(\ut+w_0)(\rho_0+\rho^\prime) X          $ & $(\ut+w_0) (\rho_0+\rho^\prime) h$ & 0 & $ \psi + (\ut \cdot \er) \frac{\partial p_0}{\partial r} $ \\[2mm]
\hline
\end{tabular}
\end{center}
\end{table*}

>>>>

\subsubsection{Advancing $\rho h$}
{\bf What the did before 8/6/08:}
\begin{equation}
\frac{\partial(\rho h)}{\partial t} = -\nabla\cdot\left[(\rho h)'\left(\Ubt 
+ w_0\eb_r\right)\right] - \nabla\cdot\left[(\rho h)_0^{n+\half,{\rm avg}}\Ubt\right] 
\underbrace{- \nabla\cdot\left[(\rho h)_0^{n+\half,{\rm pred}}w_0\eb_r\right] + \psi}_{\text{this term used to come in through} ~ (\rho h)_0^{n+1} - (\rho h)_0^n} + (\Ubt \cdot \er)\frac{\partial p_0}{\partial r} \enskip .
\end{equation}
{\bf What the code does now:} We would like to update the non-forcing
part of the enthalpy equation analogously to Section \ref{Advancing
rhoX_k}
\begin{equation}
\frac{\partial(\rho h)}{\partial t} = -\nabla\cdot(\rho h\Ub) = 
-\nabla\cdot\left\{\left[(\rho h)_0^{n+\half,{\rm avg}} 
+ (\rho h)'\right]\left(\Ubt + w_0\eb_r\right)\right\} + (\Ubt \cdot \er)\frac{\partial p_0}{\partial r} + \psi  \enskip .
\end{equation}

@@

\begin{table*}[h]
\begin{center}
\caption{Forcing term into {\tt make\_edge\_scal} \newline}
\begin{tabular}{c|c}
\hline
\hline
{H PRED TYPE} &   {Force} \\
\hline \\[-3mm]
1  $((\rho h)^\prime)$ &  $(\Ubt \cdot \er) \frac{\partial p_0}{\partial r} - 
 (\rho h)^\prime \; \nabla \cdot (\Ubt+w_0 \er) - 
 \nabla \cdot (\Ubt (\rho h)_0) + \nabla \cdot \kth \nabla T$ \\[2 mm]
2  $(h)$ & $\frac{1}{\rho} \left [\psi + (\Ubt \cdot \er)
  \frac{\partial p_0}{\partial r} + \nabla \cdot \kth \nabla T \right ]$ \\[2 mm]
3  $(T)$ & $\frac{1}{\rho c_p} \left \{ (1 - \rho h_p) 
   \left [\psi + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r} \right ] \nabla \cdot \kth \nabla T \right \}$ \\[2 mm]
4  $(T)$ & $\frac{1}{\rho c_p} \left\{ (1 - \rho h_p) \left [\psi + (\Ubt \cdot \er)
\frac{\partial p_0}{\partial r}\right ] \nabla \cdot \kth \nabla T \right\}$ \\[2 mm]
\hline
\end{tabular}
\end{center}
\end{table*}

@@

\begin{table*}
\begin{center}
\caption{Quantity that is created in {\tt mkflux} and passed into {\tt update\_scal}\newline\
}
\begin{tabular}{c|c|c|c|c}
       &            &              &\multicolumn{2}{c}{Forcing Term} \\
{type} & {Species } & {$(\rho h)$} & {$(\rho X)$} & {$(\rho h)$} \\
\hline 
1 & $(\Ubt+w_0)(\rho_0+\rho^\prime) X          $ & $(\Ubt+w_0)\left [(\rho h)_0 + (\rho h)^\prime\right]$ & 0 & $ \psi + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r} $ \\[2mm]
2 & $(\Ubt+w_0)(\rho_0+\rho^\prime) X          $ & $(\Ubt+w_0) (\rho_0+\rho^\prime) h$ & 0 & $ \psi + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r} $ \\[2mm]
3 & $(\Ubt+w_0)(\rho_0+\rho^\prime) X          $ & $(\Ubt+w_0)\left [(\rho h)_0 + (\rho h)^\prime\right]$ & 0 & $ \psi + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r}$ \\[2mm]
4 & $(\Ubt+w_0)(\rho_0+\rho^\prime) X          $ & $(\Ubt+w_0) (\rho_0+\rho^\prime) h$ & 0 & $ \psi + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r} $ \\[2mm]
\hline
\end{tabular}
\end{center}
\end{table*}
